---
title: "Mythic Play Example"
output: github_document
---

```{r}
library(RPGTips)
seed_counter <- 777
```

# Scene 1

Setting: Norvos is in a tavern.

## Opening Scene

Why is Norvos in this tavern?

```{r}
roll_table(gme_detail_check)
```
Who is he trying to disfavor?

```{r}
roll_table(gme_description_table)
```

Is he pursuing someone bad?

```{r}
roll_table(gme_fate_check)
```

Is it a man?

```{r}
roll_table(gme_fate_check)
```

Why is he pursuing this woman?
```{r}
roll_table(gme_actions_table)
```

He is pursuing a witch who grants wishes to people and then takes their souls as
a payment. Norvos' daughter's soul was taken. He found her and fought her, but
she fled. He tracked her and found her in this village in the forest.

## Scene setting

NPCs:
- The witch.
- Norvos' daughter.

Thread:
- Find and kill the witch.

Setting: Norvos has arrived in the village tavern after a long trip through the forest.

Chaos Factor: 5.

## Scene Development

We first check if the scene is altered or interrupted rolling a 1d10 and comparing
it against the Chaos Factor.
```{r}
set.seed(seed_counter)
roll(1, 10)
```

As it´s lower and odd, the scene is altered: the tavern is empty. Does it look abandoned?

```{r}
roll_table(gme_fate_check)
```

The tavern is extremely full of people having dinner and lively conversations.
The random event...
```{r}
roll_table(gme_event_check)
```
```{r}
roll_table(gme_description_table)
```

An old, ugly woman with a revealing dress gets too close to him and offers to have
a night he won't remember for just a few coins. Norvos rejects her politely and
gets close to the bar to try to get a room for the night. How does the bartender look?

```{r}
roll_table(gme_detail_check)
```

*A result that favors NPC will be interpreted as favoring the Witch. So how does someone look to be favorable to a witch? As someone that would sell his soul for a wish. He is very greedy! He looks like a bulky, brawny, bald guy with lots of fake jewelry*

The bartender greets Norvos with a slimy smile, asking him what he is doing in Oxland. 

*To summarize how the conversation goes, I will roll charisma*

```{r}
set.seed(seed_counter)
roll(1,20)
```

Norvos talks about his interest in staying for a long time at the inn, which sparks the greed of our friend, **Subild**. He's not here to make friends, though, so he asks him right away about the Witch. Does he react positively?
```{r}
roll_table(gme_fate_check)
```
What does he know?

```{r}
roll_table(gme_detail_check)
```

*I will ignore that result*

Does he know where the witch lives?

```{r}
set.seed(seed_counter)
sample(c("Yes", "No", "Doesn´t know", "Prefers to stop talking"), size = 1)
seed_counter <- seed_counter + 1
```

Does he know how to find her?

```{r}
set.seed(seed_counter)
sample(c("Yes", "No", "Doesn´t know", "Prefers to stop talking"), size = 1)
```

Who knows about her?

```{r}
roll_table(gme_description_table)
```

The Glass Enchanter may know about her! He's always dabbling into spooky stuff with his magic.  He lives in a hut in the forest, past the village, close to the Black Mountain, along the River Tamors. Everything is engulfed in the Hollow Woods.

# Scene 2

## Setting

### NPCS

- The Witch.
- Norvos' daughter.
- Subild.
- The Glass Enchanter.
- People of Oxland.

### Threads

- Find and kill the Witch.
- Find the Glass Enchanter.





















