---
title: "Mythic Play Example"
output: github_document
---

```{r}
library(RPGTips)
seed_counter <- 777
```

# Scene 1

Setting: Norvos is in a tavern.

## Opening Scene

Why is Norvos in this tavern?

```{r}
roll_table(gme_detail_check)
```

Who is he trying to disfavor?

```{r}
roll_table(gme_description_table)
```

Is Norvos evil?

```{r}
roll_table(gme_fate_check)
```

Is it a man?

```{r}
roll_table(gme_fate_check)
```


Why is he pursuing this woman?
```{r}
roll_table(gme_actions_table)
```

He is pursuing a witch who grants wishes to people and then takes their souls as a payment. Norvos' daughter's soul was taken. He found her and fought her, but she fled. He tracked her and found her in this village in the forest.

## Scene setting

NPCs:
- The witch.
- Norvos' daughter.

Thread:
- Find and kill the witch.

Setting: Norvos has arrived in the village tavern after a long trip through the forest.

Chaos Factor: 5.

## Scene Development

We first check if the scene is altered or interrupted rolling a 1d10 and comparing it against the Chaos Factor.

```{r}
set.seed(seed_counter)
roll(1, 10)
```

As it´s lower and odd, the scene is altered: the tavern is empty. Does it look abandoned?

```{r}
roll_table(gme_fate_check)
```

There are still drinks and food in plates in most of the tables, but there is not a soul to be found.

```{r}
roll_table(gme_event_check)
```
```{r}
roll_table(gme_description_table)
```

The witch seems to have just passed around the city and people were actually hiding! Once the tavern door opens and people see that it´s a foreigner, they sigh, relaxed, and go to meet him. Norvos tries to befriend them to get them to talk about the witch. 

*Charisma check*

```{r}
set.seed(seed_counter)
roll(1,20)
```

*To generate what the people know about the witch, I will roll a detail check*

```{r}
roll_table(gme_detail_check)
```

They respect her! She is the village protector. She's made a deal with them, in which they don't bother her and she protects the village from intruders and wild animals.

*Now Norvos has two options: either he declares openly he wants to know where she lives or he tries to get a room for the night and he will explore during the next day, safely knowing that the witch lives around the village. What will he do (1-5: ask for the witch, 6-10: get a room for the night)?*

```{r}
set.seed(seed_counter)
roll(1,10)
```
*He will get a room!*

He pays for a room for three days, hoping to finish this whole ordeal in less than that.

*Scene finished! Chaos Factor goes down to 4*

# Scene 2

## Scene Setting

### NPCs

- The witch.
- Norvos' daughter.
- People from Oxland.

### Threads

- Find the witch and recover his daughter's soul.





